---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  dpi = 400
)

set.seed(1)
```

# ggchameleon <img src="man/figures/logo.svg" align="right" height="139"/>

<!-- badges: start -->

<!-- badges: end -->

ggchameleon allows you to write standard [ggplot2](https://cran.r-project.org/web/packages/ggplot2/index.html) syntax while automatically theming your plots with user-specified configurations. ggchameleon balances unobtrusiveness with reproducibility, allowing the user to save a `chameleon.yml` file which stores customized ggplot theming without requiring the user to write extra code to fetch this theming.

## Installation

You can install the development version of ggchameleon from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("aarongraybill/ggchameleon")
```

## Design Principle

ggchameleon gets its name from two key design principles:

1.  The chameleon's ability to change colors at will
2.  The chameleon's ability to blend into the background of its environment.

On the color changing side, ggcchameleon allows the user to flexibly change their charts' theme elements (color, font, size of lines, etc.). ggchameleon is written to make these changes reproducible and easy to access with the `save_configs` function.

However, much a like a real chameleon in dense foliage, ggchameleon is very hard to spot in your code! ggchameleon both reduces boilerplate and maintains compatability with standard `ggplot2`. In fact, when used as intended, the only place ggchameleon appears in your scripts is `library(ggchameleon)`{.R}. All of the theming is loaded on startup from your configurations or the package defaults. If you were to remove the `library(ggchameleon)`{.R} at the beginning of your code, you would produce plots with exactly the same information, now in the default ggplot theme.

## Basic Usage

First, here's the look of a standard ggplot:

```{r example,message=FALSE}
library(ggplot2)
library(dplyr)

d <- diamonds |> slice_sample(n = 100)
p <- ggplot(d) +
  geom_point(aes(x = carat, y = price, color = price)) +
  ggtitle("My Cool & Informative Plot",
          subtitle = "With an even cooler subtitle!")
p
```

Now, if we load the ggchameleon package we can immediately see a change in how the plot looks:

```{r add_ggchameleon}
library(ggchameleon)
p
```

However, ggchameleon is intended to allow the user to configure their own style.
In the plot above, the color goes from dark blue, to orange, to yellow. If you 
change the `"intermediate"` color, then you can make your color gradient go from
the same dark blue to yellow, but now through green instead of orange.

```{r altering_ggchameleon}
edit_the_main_palette(intermediate = "darkgreen")
p
```

Notice that without having to specify a different `scale_color_continuous`, we were able to drastically change the colors of the legend. This is where ggchameleon does the heavy lifting. It finds the parts of your theme that use the `intermediate` color and updates all such instances to use the new color.

```{r editing_fonts}
edit_the_fonts(sans="Creepster")
p
```

We can also edit elements of the theme that we apply to each plot by default, for example:

```{r editing_theme}
edit_the_theme(legend.position = "bottom",
                             legend.direction = "horizontal")

p
```

If you're lacking color inspiration, ggchameleon provides a function to
automatically generate a new color palette.

```{r huemint_and_font_shuffle}
huemint_randomize(auto_accept = TRUE)
```

When run with `auto_accept = FALSE` (the default), the function will preview the
new colors as above, and then give you the option to reject or accept the
proposed theme. ggchameleon uses an API from [huemint.com](huemint.com) to
generate the color scheme. The colors on Huemint are generated by a Machine
Learning model that is trained on the design decisions of web developers, so the
palettes generated are often more visually appealing than randomly drawing
colors from a hat.

But once we've accepted the theme, we can see that it has overhauled the colors:

```{r}
# Show the new colors from Huemint
p
```


## Wrapping Up For Next Time

Now that we've edited the theming to our heart's content, we can save these modifications for next time we use this project. If we run the following, we will save a file, `chameleon.yml` which will be automatically applied the next time we load this project and use `library(ggchameleon)`.

```{r save_theme,eval=FALSE}
save_configs()
```

By default, `save_configs()` stores `chameleon.yml` in your current working directory. If you're using an R project (ie if you have a .Rproj file), and then `chameleon.yml` will likely be saved at the same level as your `.Rproj`. This is useful because then all of the other scripts under this R project will automatically have your saved configurations applied.
