---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ggchameleon <img src="man/figures/logo.svg" align="right" height="139"/>

<!-- badges: start -->

<!-- badges: end -->

ggchameleon allows you to write standard [ggplot2](https://cran.r-project.org/web/packages/ggplot2/index.html) syntax while automatically theming your plots with user-specified or algorithmically determined colors and fonts. ggchameleon balances unobtrusiveness with reprodroducibility, allowing the user to save a `chameleon.yml` file which stores customized ggplot theming without requiring the user to write extra code to fetch this theming.

## Installation

You can install the development version of ggchameleon from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("aarongraybill/ggchameleon")
```

## Design Principle

ggchameleon gets its name from two key design principles:

1.  The chameleon's ability to change colors at will
2.  The chameleon's ability to blend into the background of its environment.

On the color changing side, ggcchameleon allows the user to flexibly change theme elements (color, font, size of lines, etc.). ggchameleon is written to make these changes reproducible and easy to access with the `save_current_theme` function.

However, much a like a real chameleon in dense rain forest foliage, ggchameleon is very hard to spot in your code! ggchameleon both reduces boilerplate and maintains compatability with standard `ggplot2`. In fact, when used as intended, the only place ggchameleon appears in your scripts is `library(ggchameleon)`{.R}. All of the theming is loaded on startup from your configurations or the package defaults. If you were to remove the `library(ggchameleon)`{.R} at the beginning of your code, you would produce plots with exactly the same information, now in the default ggplot theme.

## Basic Usage

First, here's how a standard ggplot2 looks:

```{r example,message=FALSE}
library(ggplot2)
library(dplyr)

set.seed(1)
d <- diamonds |> slice_sample(n=1000)
ggplot(d)+
  geom_point(aes(x=carat,y=price,color=cut))+
  ggtitle("My Cool Title")
```

Now, if we load the ggchameleon package we can immediately see a change in how the plot looks:

```{r add ggchameleon}
library(ggchameleon)
ggplot(d)+
  geom_point(aes(x=carat,y=price,color=clarity))
```

But the real magic of ggchameleon comes when we wish to alter the default ggchameleon parameters:

```{r altering ggchameleon}
ggchameleon:::edit_the_main_palette(main = "#FF0000")
ggplot(d)+
  geom_point(aes(x=carat,y=price,color=clarity))
```

`main` in the above example is the main color used throughout the plot and in the title text's color. We can edit any of the colors, but we can also edit any of the fonts, as seen below:

```{r editing fonts}
ggchameleon:::edit_the_fonts(sans="Press Start 2P")
ggplot(d)+
  geom_point(aes(x=carat,y=price,color=clarity))
```

We can also edit elements of the theme that we apply to each plot by default, for example:

```{r editing theme}

ggchameleon:::edit_the_theme(legend.position = "None")

ggplot(d)+
  geom_point(aes(x=carat,y=price,color=clarity))
```

Now that we've edited the theming to our heart's content, we can save these modifications for next time we use this project. If we run the following, we will save a file, `chameleon.yml` which will be automatically applied the next time we load this project.

```{r save theme,eval=FALSE}
ggchameleon:::save_current_theme()
```
